\section{Data Quality and Missing Values}

\subsection*{Overview}

The dataset comprises 1\,304 daily observations across 20 time series, covering
the period January 2018 to April 2023. Not all series are available for every
trading day: holidays, differing market calendars (US vs.\ European), and
data-provider coverage gaps introduce missing values.

\subsection*{Missing-Value Statistics}

Table~\ref{tab:missing} summarises the number and proportion of missing
observations for each series, sorted by the percentage of missing data.

\begin{table}[H]
  \centering
  \caption{Missing observations per series.}
  \label{tab:missing}
  \small
  \begin{tabular}{lrrr}
    \toprule
    \textbf{Series} & \textbf{Missing} & \textbf{Available} & \textbf{\% Missing} \\
    \midrule
    FR5BEI       & 1\,112 &   192 & 85.3 \\
    ESTR         &   395 &   909 & 30.3 \\
    SOFR         &    57 & 1\,247 &  4.4 \\
    UST10        &    55 & 1\,249 &  4.2 \\
    UST2         &    55 & 1\,249 &  4.2 \\
    US5BEI       &    55 & 1\,249 &  4.2 \\
    CDX IG       &    54 & 1\,250 &  4.1 \\
    CDX HY       &    54 & 1\,250 &  4.1 \\
    S\&P         &    46 & 1\,258 &  3.5 \\
    ITRX IG      &    42 & 1\,262 &  3.2 \\
    ITRX XO      &    42 & 1\,262 &  3.2 \\
    VIX          &    39 & 1\,265 &  3.0 \\
    DEM2         &    24 & 1\,280 &  1.8 \\
    DEM10        &    23 & 1\,281 &  1.8 \\
    ESTX600      &    19 & 1\,285 &  1.5 \\
    CO           &    12 & 1\,292 &  0.9 \\
    EURUSD       &     0 & 1\,304 &  0.0 \\
    EURUSD3mBS   &     0 & 1\,304 &  0.0 \\
    USYC         &     0 & 1\,304 &  0.0 \\
    DEYC         &     0 & 1\,304 &  0.0 \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection*{Key Observations}

\begin{itemize}
  \item \textbf{FR5BEI (French 5yr inflation breakeven):} 85.3\% of
    observations are missing. With only 192 usable data points out of 1\,304,
    this series cannot support reliable statistical analysis. It is therefore
    \textbf{excluded from all analyses} in both the main report and this
    sensitivity document.
  \item \textbf{ESTR (Euro short-term rate):} 30.3\% missing. ESTR was
    introduced by the ECB in October 2019, so observations before that date are
    unavailable. Any model that includes ESTR is effectively restricted to a
    roughly three-year subsample.
  \item \textbf{US rates, CDS indices, and equity series (3--4\% missing):}
    these gaps align with US and European public holidays and occasional
    data-feed outages. Their impact on analysis is modest.
  \item \textbf{EURUSD, EURUSD3mBS, USYC, DEYC:} fully populated with no
    missing values.
\end{itemize}

\subsection*{Treatment}

The following approach is applied consistently throughout the main report and
this sensitivity document:

\begin{enumerate}
  \item \textbf{Pairwise (listwise per analysis) deletion.} For each specific
    computation --- whether a correlation, regression, or rolling-window
    estimate --- only dates for which \emph{all} required series are
    simultaneously available are used. This avoids imputing values for
    financial time series where interpolation could distort volatility
    clustering, jump dynamics, and cross-sectional relationships.

  \item \textbf{No forward-filling or interpolation.} Given that the missing
    observations predominantly correspond to genuine market closures (holidays),
    carrying forward the previous day's close would artificially inject zero
    returns on non-trading days. This would understate realised volatility and
    bias correlation estimates toward zero.

  \item \textbf{Impact on model selection.} Following the exclusion of FR5BEI,
    the InflationMacro candidate model is reduced to four regressors (\(\Delta
    CO\), \(\Delta US5BEI\), \(\Delta UST2\), \(\Delta DEM2\)). The high
    proportion of missing values in ESTR (30.3\%) also materially reduces the
    effective sample for any model that includes it: the FXBasisPolicy
    specification retains only 834 observations after differencing, limiting
    the reliability of its rolling-window estimates.
\end{enumerate}
